\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Proof of Concept: Design}
\author{Thomas Kongonis}
\date{September 2019}

\begin{document}

\maketitle

\tableofcontents

\section{Aims}

\begin{itemize}

\item{To continue on from the scoping and elaboration phases, this design will further specify the necessary components of the project in a more concise and developed manner.}

\end{itemize}



\section{User Stories}


\subsection{Primary User story}

\begin{itemize}
\item{As a student, i want to be able to view multiple translations alongside each other, so that i don't have to go searching every time i get confused with a translated term.} 

\end{itemize}


\subsection{Secondary User Story}

\begin{itemize}

\item{As a student, i want to be able to convert and tag text files in a useful way, so that i can apply this code mentioned to more than just one set of translations.}
    
    
    
\end{itemize}



\section{Acceptance Criteria}
\begin{itemize}
    \item{As stated, i should be able to:} 
\end{itemize}

\subsection{Utilising Shell Script}

\begin{enumerate}

\item{Supply a translation database of at least 5 translations}

\item{Choose a relevant chapter based upon a lack of clarity in one primary translation.}

\item{Implement the shell code with the necessary chapter in mind.}

\item{Generate the 5 relevant chapters alongside eachother.}

\end{enumerate}

\subsection{Translating and Tagging text files}

\begin{enumerate}
\item{Supply a number of translations in whatever format they are sourced in}

\item{Diagnose correct format and necessary tags}

\item{Apply these changes in a formulated and efficient way}

\item{Document and list changes and difficulties for future use.}

\item{Transfer files to a directory for usage by the created shell script.}
\end{enumerate}


\section{Quality Assurance}

\begin{itemize}
    \item{For this to be successful, it will be necessary to correctly tag and convert each translation into a usable format first, as such another aspect to the project is needed.}
    
\item{In the context of the file conversion, it will be necessary to record the way in which it was done in a coherent manner so that the process can be replicated.}

\item{For the shell script, it is necessary that the relative metadata is listed so that there is not any confusion and it can be utilised by other individuals in the future.}
\end{itemize}

\end{document}
